---
title: "36-613 Homework 5, Fall 2022"
author: 
- "[Your Name Here]"
- 'Style Guide: [insert style guide here]'
date: "Due Wednesday, Oct 5th, 2022 (11:59 PM EDT) on Gradescope"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Problem 1: The Principal Components of Coffee (55 points)

For this problem you'll work with a dataset curated via the [#TidyTuesday project](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-07-07/readme.md) containing information from the Coffee Quality Database. The following code reads in the dataset and performs some initial pre-processing:

```{r}
library(tidyverse)
coffee_ratings <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv') %>%
  filter(total_cup_points > 0)
```

a. (10pts) For this part, perform the following tasks:

+ Create a subset of the `coffee_ratings` dataset that only contains the 11 quantitative grade columns (starting with `aroma` and ending with `moisture`, see the README above for info about the columns in this dataset). Call this `coffee_quant`.

```{r}
coffee_quant <- coffee_ratings %>% 
  dplyr::select(aroma:moisture)
```

+ Run principal components analysis (PCA) on `coffee_quant`. Be sure that the columns of `coffee` are *centered* and *standardized* when you run PCA.

```{r}
coffee_pca <- coffee_quant %>% 
  prcomp(center = TRUE, scale. = TRUE)
summary(coffee_pca)
```

Then, answer the following questions: What proportion of the total variation in the data is accounted by the first principal component specifically? By the second principal component specifically? By both the first and second principal components together?

**47.27% of the total variation in the data is accounted by the first principal component specifically. And 14.92% by the second principal component specifically. And 62.19% by both the first and second principal components together.**

b. (10pts) In class we discussed using a scree plot (or *elbow plot*) to determine how many principal components should be used for visualization. For this part, create an elbow plot for these data, where the component numbers (1 through 11) are on the x-axis, and the proportion of total variation is on the y-axis.

```{r}
library(factoextra)
fviz_eig(coffee_pca, addlabels = TRUE, ncp = 11) +
  geom_hline(yintercept = 100 * (1 / ncol(coffee_pca$x)), 
             linetype = "dashed", 
             color = "darkred") +
  theme(plot.title = element_text(hjust = 0.5))
```


After you've made your plot: Based on the plot, how many principal components do you think should be used for visualizations and analyses? Provide a 1-2 sentence explanation.

**I think 3 principal components should be used for visualizations and analyses. Because the change of total variance after adding the forth PC is very small.**


c. (15pts) Use `ggplot()` to make the following scatterplots:

+ A scatterplot with the first principal component on the x-axis and the second principal component on the y-axis, with points colored by `total_cup_points`. __Choose an appropriate color gradient scale for `total_cup_points` that is different from the default.__

```{r}
coffee_pc_matrix <- coffee_pca$x
coffee <- coffee_ratings%>% 
  mutate(pc1 = coffee_pc_matrix[,1], 
         pc2 = coffee_pc_matrix[,2])
coffee %>% 
  ggplot(aes(x = pc1, 
             y = pc2)) + 
  geom_point(alpha = 0.7,
             aes(color = total_cup_points)) + 
  scale_color_gradient(low = "darkblue",
                        high = "darkorange") +
  labs(x = "PC 1", y = "PC 2",
       title = "Scatter plot") +
  theme(plot.title = element_text(hjust = 0.5))
```

+ A scatterplot with the first principal component on the x-axis and the third principal component on the y-axis, with points colored by `total_cup_points`.  __Again, choose an appropriate color gradient scale for `total_cup_points` that is different from the default.__

```{r}
coffee <- coffee_ratings%>% 
  mutate(pc1 = coffee_pc_matrix[,1], 
         pc3 = coffee_pc_matrix[,3])
coffee %>% 
  ggplot(aes(x = pc1, 
             y = pc3)) + 
  geom_point(alpha = 0.7,
             aes(color = total_cup_points)) + 
  scale_color_gradient(low = "darkblue",
                        high = "darkorange") +
  labs(x = "PC 1", y = "PC 3",
       title = "Scatter plot") +
  theme(plot.title = element_text(hjust = 0.5))
```

Then, for your each plot, discuss your main observations in 1-3 sentences. In particular: does `total_cup_points` appear to be associated with the any of the principal components you viewed in your plots?

**According to the first scatter plot and second plot, points with high PC1 tend to have smaller total_cup_points, while points with low PC1 tend to have larger total_cup_points. And the data points in the second plots are clustered into two clusters.**

d. (20pts) As discussed in lecture, principal components are not interpretable by themselves, thereby limiting the observations you can make about the data. In this part we'll explore in what ways the **first and third principal components** are related to the original variables in the data.

For this part, complete the following two tasks:

1) Use `fviz_pca_biplot()` to make a biplot of the first and third principal components (change the `axes` input to be `c(1, 3)`). When you make this plot, unfortunately, it may be difficult to see some of the variable names on the arrows; if that is the case for you, put `repel = TRUE` within `fviz_pca_biplot()`, such that you can see all of the variable names. Additionally, color the points by the `total_cup_points` variable using the `col.ind` argument. You can use the the commented out code as a template. 

After you've made the biplot, discuss in 1-4 sentences in what ways `total_cup_points` is associated with the original variables in the data.

```{r}
fviz_pca_biplot(coffee_pca,
                 # Plot PC1 and PC3
                 axes = c(1, 3),
                 # Change the alpha for the observations - 
                 # which is represented by ind
                 alpha.ind = 0.5,
                 # Modify the alpha for the variables (var):
                 alpha.var = 0.6,
                 repel = T,
                 # Set the color of the points to decades variable:
                 col.ind = coffee_ratings$total_cup_points, 
                 # Modify the color of the variables
                 col.var = "darkblue") +
   scale_color_gradient(low = "darkblue", high = "darkorange") +
   labs(color = "Total cup points") +
   theme(legend.position = "bottom",
         plot.title = element_text(hjust = .5))
```

**The higher the original variable(except for moisture) values are, the higher the total cup points are. Similarly, the lower the original variable(except for moisture) values are, the lower the total cup points are. But moisture is somehow positively correlated with total cup points.**


2) In Part C you should have used the `prcomp()` to create the principal components. After you've done that, you should be able to edit and uncomment the following line of code:

```{r}
coffee_pca$rotation
```

where `coffee_pca` is the object appropriately defined by `prcomp()`. You should be able to see an 11-by-11 matrix, where the rows correspond to the original variables and the columns correspond to the principal components. Each column represents the *linear combination* of the variables that each principal component represents (as discussed in class). In particular: Each number tells you how the variable is associated with the principal component. If a number is positive, that means cofees with a higher value of that principal component also tend to have a higher value of that variable. Similarly, if a number is negative, that means coffees with a *lower* value of that principal component tend to have a higher value of that variable.

Now look back at the first plot you made in Part C, which visualizes the first and third principal components (colored by `total_cup_points`). Given these details about the rotation matrix, discuss in 1-4 sentences in what ways `total_cup_points` is associated with the original variables in the data. Be sure to explain how you used the rotation matrix output to arrive at your answer.

```{r}
coffee_ratings %>% 
  dplyr::select(total_cup_points, aroma:moisture) %>% 
  cor()
```

**According to the rotation matrix, PC1 is negatively correlated with all original variables except for moisture. And according to the plot, PC1 is negatively correlated with total cup points. So all original variables except for moisture are positively correlated with total cup points, while moisture is negatively correlated with total cup points.**

# Problem 2: Your Shiny Project (45 points)

The goal of this problem is to help your team get started on your final project for this class. You can view your team's assigned project dataset [here](https://docs.google.com/spreadsheets/d/1XRCC8WO8O1-fy9nDf1pQ_15XxYYNGU6Z/edit?usp=sharing&ouid=110931742237993657587&rtpof=true&sd=true). __Everyone in your project group can submit the same work for this problem.__

a. (10pts) To help structure your report, you are required to come up with at least three interesting, overarching questions for your dataset that are relevant for your 36-611 RFI. For this part, similar to part (c) of problem 1 in HW4, create a plot that is relevant to one of your research questions. For this part, just include the code for making the visualization as you do traditionally in homework. You will then make this visual interactive in parts b and c. You do NOT need to write an interpretation of the plot. __Make sure it is labeled appropriatedly.__ 

```{r}
library(lubridate)
# Get the Data
spotify_songs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-21/spotify_songs.csv')

year.temp <- year(as.Date(spotify_songs$track_album_release_date))
spotify_songs$decade <- year.temp - year.temp %% 10

# PLotting
spotify_songs[which((spotify_songs$decade == 2000) & (spotify_songs$playlist_genre == "pop")),] %>% 
  ggplot(aes(x = playlist_subgenre, 
             y = energy,
             fill = playlist_subgenre)) + 
  geom_violin(alpha = .5) + 
  geom_boxplot(width = .2, alpha = .5) +
  labs(x = "Genre",
       y = "Energe",
       title = "Distribution of Energe of different Genres") +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_flip()

library(shiny)
```

b. (30pts) Create a Shiny app that converts your graph in part (a) to be reactive to __at least 3 widgets__ for the user to interact with the graph. Here are useful resources for you to look at for making Shiny apps and the various kinds of widgets:

+ [Shiny tutorials](https://shiny.rstudio.com/tutorial/)

+ [Shiny Gallery](https://shiny.rstudio.com/gallery/)

+ [Shiny cheatsheet](https://shiny.rstudio.com/images/shiny-cheatsheet.pdf)

+ [Shiny Widgets Gallery](https://shiny.rstudio.com/gallery/widget-gallery.html)

You do NOT need to turn in any code for this part, because we will grade your Shiny app based on you correctly following the directions in part c.

c. (5pts) Follow [these directions by RStudio](https://shiny.rstudio.com/articles/shinyapps.html) to host your Shiny app created in part b on [shinyapps.io](https://www.shinyapps.io/?_ga=2.203244757.538422124.1664324851-1806775795.1664324851). All you have to do for this part is share the link for your Shiny app:

**https://yipu.shinyapps.io/Project/**


